% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.1 distribution.
%   Version 4.1r of REVTeX, August 2010
%
%   Copyright (c) 2009, 2010 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
10.5pt,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{array}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\usepackage{xeCJK}
%\setCJKmainfont[ItalicFont={KaiTi}, BoldFont={KaiTi}]{KaiTi}
\usepackage{textcomp}
\usepackage{chemfig}
\usepackage[version=4]{mhchem}
\usepackage{fontspec}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{xcolor} % 定制颜色
\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}
\lstset{
backgroundcolor=\color{white},      % choose the background color
basicstyle=\footnotesize\ttfamily,  % size of fonts used for the code
columns=fullflexible,
tabsize=4,
breaklines=true,               % automatic line breaking only at whitespace
captionpos=b,                  % sets the caption-position to bottom
commentstyle=\color{mygreen},  % comment style
escapeinside={\%*}{*)},        % if you want to add LaTeX within your code
keywordstyle=\color{blue},     % keyword style
stringstyle=\color{mymauve}\ttfamily,  % string literal style
frame=single,
rulesepcolor=\color{red!20!green!20!blue!20},
% identifierstyle=\color{red},
language=Mathematica,
}

\usepackage[normalem]{ulem}

\newcommand{\chuhao}{\fontsize{42pt}{44.9pt}\selectfont}    % 初号, 1.5倍行距
\newcommand{\xiaochu}{\fontsize{30pt}{40pt}\selectfont}    % 小初, 1.5倍行距
\newcommand{\yihao}{\fontsize{26pt}{36pt}\selectfont}    % 一号, 1.4倍行距
\newcommand{\erhao}{\fontsize{22pt}{28pt}\selectfont}    % 二号, 1.25倍行距
\newcommand{\xiaoer}{\fontsize{18pt}{18pt}\selectfont}    % 小二, 单倍行距
\newcommand{\sanhao}{\fontsize{16pt}{24pt}\selectfont}    % 三号, 1.5倍行距
\newcommand{\xiaosan}{\fontsize{15pt}{22pt}\selectfont}    % 小三, 1.5倍行距
\newcommand{\sihao}{\fontsize{14pt}{21pt}\selectfont}    % 四号, 1.5倍行距
\newcommand{\sihaox}{\fontsize{14pt}{28pt}\selectfont}    % 四号, 1.5倍行距
\newcommand{\banxiaosi}{\fontsize{13pt}{19.5pt}\selectfont}    % 半小四, 1.5倍行距
\newcommand{\xiaosix}{\fontsize{12pt}{24pt}\selectfont} 	% 小四, 1.5倍行距
\newcommand{\xiaosi}{\fontsize{12pt}{18pt}\selectfont}     
\newcommand{\dawuhao}{\fontsize{11pt}{11pt}\selectfont}    % 大五号, 单倍行距
\newcommand{\wuhao}{\fontsize{10.5pt}{10.5pt}\selectfont}    % 五号, 单倍行距
\newcommand{\xiaowu}{\fontsize{9pt}{9pt}\selectfont}    % 五号, 单倍行距

%\usepackage[fntef]{ctexcap}
%\CTEXsetup[number={\chinese{section}、},format={\Large\bfseries}]{section}
%\setCJKfamilyfont{fangsong}{FangSong}                      %仿宋2312 fs  
%\newcommand{\fangsong}{\CJKfamily{fangsong}}  

\usepackage{wrapfig}
\usepackage{fancyhdr}
\usepackage{fancybox}   






\newcommand{\bra}[1]{\langle #1 |}
\newcommand{\ket}[1]{| #1 \rangle}
\newcommand{\bracket}[2]{\langle #1 | #2 \rangle}
\newcommand{\bracketl}[3]{\langle #1 | #2 | #3 \rangle}
\newcommand{\func}{\mathrm \,}
\newcommand{\define}[2]{
	\begin{definition}
	\begin{description}
	\item[#1]
	#2
	\end{description}
	\end{definition}
}

\newcommand{\sch}{Schr\"odinger}
\newcommand{\grad}{\nabla}
\newcommand{\ueq}{\neq}
\newcommand{\celsius}{\ensuremath{^\circ\hspace{-0.09em}\mathrm{C}}}
\newcommand{\unit}[2]{$#1 \, \mathrm{#2}$}

\begin{document}

%\preprint{APS/123-QED}

\title{A title here}% Force line breaks with \\
%\thanks{A footnote to the article title}% give thanks

\author{Rui Li}
 %\altaffiliation[Also at ]{Physics Department, XYZ University.}%Lines break automatically or can be forced with \\
%\author{Second Author}%
%\email{3160102098@zju.edu.cn}
\affiliation{%
 Qiushi science class (chemistry)\\
 Chu Kochen Honor College
}%

%\collaboration{MUSO Collaboration}%\noaffiliation

%\author{Zong Wei Huang}
% \homepage{http://www.Second.institution.edu/~Charlie.Author}
%\affiliation{
% Second institution and/or address\\
% This line break forced% with \\
%}%
%\affiliation{
%Qiushi science class (chemistry)\\
% Chu Kochen Honor College
%}%
%\author{Delta Author}
%\affiliation{%
% Authors' institution and/or address\\
% This line break forced with \textbackslash\textbackslash
%}%

%\collaboration{CLEO Collaboration}%\noaffiliation

%\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
Abstract inserted here.
\begin{description}
\item[Keywords]
Some keywords intended.
\end{description}
\end{abstract}

%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
                             % Classification Scheme.
%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle

\tableofcontents

\section{Introduction}
Electrode potential is derived from the thermodynamics' second law that for an arbitrary process occurred in a system, the maximum non-volume work is given by
\begin{equation}
W_{\text{non-}pV} \leq  - \Delta G,
\end{equation}
and for a process involving electron transfer, electric work dominates the non-volume work. Faraday pointed out its linearity towards the amount of electrons transferred, as is natural in electric circuits,
\begin{equation}
W_{\text{non-}pV,\text{max}} = - \Delta = nFE
\end{equation}
where $n$ is the total amounts of electrons transferred, $F$ the Faraday constant representing electric charges of 1 mol electrons, and $E$ represents the electric potential in the circuit provided by the reaction. Thus it is evident that Any reaction that involves electron transfer and a decrease in Gibbs free energy can be applied as an electric power source.

Nernst equation is deduced in the system of chemical equilibrium, from the equation of which was deduced in the former report,
\begin{equation}
 \Delta G_m = \Delta G^\ominus +  RT \ln Q = \Delta G_m^\ominus + RT \ln{\frac{\alpha_\text{product}^{c_i}}{\prod\alpha_\text{reactant}^{c_j}}}
 \end{equation}
 and when decomposing it into half-electrode reactions for oxidants and redox, combining it with the Faraday equation, it is deduced that
 \begin{equation}
 E_\text{red} = E^\ominus_\text{red} -\frac{RT}{zF} \ln{Q'} = E^\ominus_\text{red} - \frac{RT}{zF} \ln{\frac{\alpha_\text{red}}{\alpha_\text{Ox}}}
\end{equation}
where $\alpha$ represents the fugacity of the matter in the solution, and $z$ the amount of electrons per mole of reaction that transferred. The same can be deduced for the redox reaction.

According to Kirchhoff's circuit laws, the current will cause an decrease in the measurement of the potential of a battery using simple electric circuits due to inevitable resistance for the battery. Thus an apparatus that can measure a potential with no current through the battery needs to be adopted, linear sweep vltammetry as one of the examples. The apparatus in this experiment is much simpler, involving several variable resistances with battery that provides a standard electric potential, which can help deduce the electric potential of the target battery according to the Kirchhoff's circuit laws.

\section{Methods and procedures}
A series of standard solution of \ce{KCl} and standard solution of \ce{AgNO3} in different concentrations was prepared respectively. Each battery consists of a pair from four electrodes - saturated calomel electrode in saturated KCl solution, silver chloride electrode in different concentration of \ce{KCl} solution, silver electrode in different concetration of \ce{AgNO3} solution - is measured using Model UJ-25 high voltage DC potentiometer. The electrric potential of battery that consists of saturated calomel electrode in saturated KCl solution and silver chloride electrode in 0.0900 M of KCl solution is measured at different temperatures. 

\section{}




\end{document}
